Cross-Validation Default

### 2024-02-19 minos/validation/cross_validation_default.Rmd
Fixed cv transitions targets in transition Makefile. Also changed the year for transition models for housing_tenure and financial_situation due to a change in the factor levels of housing_tenure in 2019. This meant that transition models where housing_tenure is a predictor (or an outcome) have to be pre-2019 for cross-validation (due to cv starting in 2015)

```{r}
raw.nkids_max <- raw %>%
  dplyr::select(pidp, time, nkids) %>%
  group_by(time) %>%
  summarise(max_nkids = max(nkids)) %>%
  mutate(source = 'final_US')

cv.nkids_max <- cv %>%
  dplyr::select(pidp, time, nkids) %>%
  group_by(time) %>%
  summarise(max_nkids = max(nkids)) %>%
  mutate(source = 'baseline_output')

>>>>

```{r}
raw.nkids_max <- raw %>%
  dplyr::select(time, nkids) %>%
  group_by(time) %>%
  summarise(max_nkids = max(nkids)) %>%
  mutate(source = 'final_US')

cv.nkids_max <- cv %>%
  dplyr::select(time, nkids) %>%
  group_by(time) %>%
  summarise(max_nkids = max(nkids)) %>%
  mutate(source = 'baseline_output')
